What's hot and what's not:\\Windowed developer topic analysis

### 2009-04-11 lda-paper.tex
what

The second largest trend was during the month of March 2001 relating
to incremental building and the porting of developer Konstantin's
Solaris port of the Firebird build files. The third largest trend was
about JDBC, which is how Firebird and Java communicate.  Other trends
included topics regarding AIX PPC compilation, updating the build
process, internationalization and UTF8, Darwin build support and bug
fixing.

>>>>

The second largest trend was during the month of March 2001. It was
related to incremental building and the porting of developer
Konstantin's Solaris port of the Firebird build files. The third
largest trend was about JDBC, which is how Firebird and Java
communicate.  Other trends included topics regarding AIX PPC
compilation, updating the build process, internationalization and
UTF8, Darwin build support and bug fixing.
